An inquiry into the influence of parallelism and the choice of random engines on the runtime and results of Stride

### 2018-03-10 assets/src/week4/paper/main.tex
4->6
Add more script from past week + update URL's in Paper

The analysis described in this section was performed on a 32 core AMD machine. Therefore the tests were executed with a maximum of 32 threads, which is a reasonable maximum for any workstation at the time of writing. By using a Bash-script\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/597e9d14356a40f10c52dbd789ce495f0891720e/assets/src/week3/bench.sh}} % TODO update links to website
the Stride tests were run with an increasing amount of threads, starting at 1 up to 32.

@@

Using a Python3 script\footnote{\url{https://github.com/LEDfan/Bachelorproef/blob/b8b67f7083ba8a523bdb16f0c6fd0fdfeea7dacf/assets/src/week3/random_engines.py}} % TODO update links to website
the simulation was run using the different random engines, at the same time measuring the running time.

@@

\sidebyside[!hbt][fig:threads:scatter][fig:threads:boxplot]
    {Connected scatter plot}
    {images/performance_scatter.png}
    {Boxplot}
    {images/boxplot_performance.png}
    {Running time in function of number of threads}
    {fig:threads}
\subsection{Influence of random engine}
The engine which needs the least amount of time is the \texttt{lgc64} engine, the \texttt{yarn3} engine requires the most amount of time. The difference in time is 60 seconds when running the tests 15 times, which means that for one run the difference is only about 6 seconds. Thus there isn’t a big difference. A complete comparison of running times can be found in \cref{fig:engine:running}.
The distribution analysis of the results with different random engines was done with 100 data points for each random engine. While this is still a relatively small sample size, much larger sample sizes were not feasible due to the time requirements to run them all.

@@

A few of the plots can be seen in \cref{fig:normality}, and for those who would like to see more of them, they can be generated with the script and datafiles found at \url{TODO TODO TODO}. % TODO: update url once published to gh-pages

>>>>

The analysis described in this section was performed on a 32 core AMD machine. Therefore the tests were executed with a maximum of 32 threads, which is a reasonable maximum for any workstation at the time of writing. By using a Bash-script\footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/bench.sh}} % TODO update links to website
the Stride tests were run with an increasing amount of threads, starting at 1 up to 32.

@@

Using a Python3 script\footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/random\_engines.py}} 
the simulation was run using the different random engines, at the same time measuring the running time.

@@

\sidebyside[!hbt][fig:threads:scatter][fig:threads:boxplot]
    {Connected scatter plot}
    {images/performance_scatter.png}
    {Boxplot}
    {images/boxplot_performance.png}
    {Running time in function of number of threads}
    {fig:threads}
\subsection{Influence of random engine}
The engine which needs the least amount of time is the \texttt{lgc64} engine, the \texttt{yarn3} engine requires the most amount of time. The difference in time is 60 seconds when running the tests 15 times, which means that for one run the difference is only about 4 seconds. Thus there isn’t a big difference. A complete comparison of running times can be found in \cref{fig:engine:running}.
The distribution analysis of the results with different random engines was done with 100 data points for each random engine. While this is still a relatively small sample size, much larger sample sizes were not feasible due to the time requirements to run them all.

@@

A few of the plots can be seen in \cref{fig:normality}, and for those who would like to see more of them, they can be generated with the script and datafiles found at our website \footnote{\url{https://ledfan.github.io/Bachelorproef/assets/src/week4/random\_engines\_stats.py}}.
